Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-27 be.tex
more changes to the Bernoulli appendix.

\begin{align}
\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \left(\frac{v^2}{2} + \Phi
    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi
\label{eq:enCons}
\end{align}

Where $\kew=v_w^2+\sigma^2\simeq v_w^2+\frac{G M_{\rm enc}(r)}{r}$ and
$\Menc$ is the sum of the black hole mass and the stellar mass.

@@

Then one obtains for the mass flux, $f$

\begin{align}
 f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right]
 \label{eq:massFlux}
\end{align}

@@

\begin{align}
\Phi= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\rs} \rhostar(dr') r'
dr'.
\label{eq:Phi}
\end{align}

Note our unconventional choice of gauge: the upper limit of the
integral on the right hand side is $\rs$ whereas conventionally the
upper limit is taken to be $\infty$. This means that our definition
will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
gauge invariant.

Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
and~\eqref{eq:Phi}, we may obtain an expression for the enthalpy,
$\ke+\gammaf \frac{p}{\rho}$ of the gas inside of the break radius
$\rb$.

\begin{align}
  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} = \frac{G \Mbh}{x \rs} +
  \frac{G
    M_\star}{x \rs} - U_o \frac{x^{2-\delta}-1}{2-\delta}\nonumber\\
  &-U_o\left[\frac{1}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}

@@

\begin{multline}
  \frac{v^2}{2}+\gammaf \frac{p}{\rho}
=\frac{G \Mbh}{\rs} 
\biggl[
  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}+\frac{1}{x}+\frac{w}{x}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -w \frac{3 -\delta}{2 -\delta} x^{2 -\delta}
  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr].
\label{eq:enthAnal}
\end{multline}

@@

For sufficiently large radii ($x$), the expression above always
becomes negative, which means that a break in the stellar density
profile is necessary in order to obtain an outflow. For a given
$\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such that if
$\zeta>\zeta_c$, an outflow will be possible from any
radius. On the other hand if $\zeta<\zeta_c$, then there is a
minimum radius from which an outflow is possible, so that we have a
constraint on $\rs/\rsoi$.

For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
($v_w\simeq\sigma_0$).  On the other hand for core galaxies
($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$. We also
find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
less than this value the gas enthalpy would become negative inside of
the break radius which is clearly unphysical.  This may be roughly
approximated using (see Fig.~\ref{fig:rbRinf})

\begin{align}
&\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
&\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
\label{eq:rsRinfCrit}
\end{align}

\begin{figure}
\includegraphics[width=\columnwidth]{rbRinf.pdf}
\caption{\label{fig:rbRinf} Mininmum value for ratio of the stagnation
  radius to the influence radius, $\rs/\rsoi$ for core galaxies
  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
  positive out to the break radius $\rb$. The solid lines correspond
  to the constraint computed numerically from
  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
  x-intercept of each curve corresponds to the critical $\zeta$,
  $\zeta_c$ above which an outflow is possible from any radius}
\end{figure}

>>>>

\begin{align}
\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \left(\frac{v^2}{2} + \Phi
    + \gammaf \frac{p}{\rho}\right) \right) = q \kew + q \Phi,
\label{eq:enCons}
\end{align}

Where $\vw^2=v_w^2+\sigma^2= v_w^2+\frac{3}{\Gamma+2}\frac{G
  \Mbh}{r}+\sigma_0^2$.

@@

Then one obtains for the mass flux, $f=r^2 \rho v$,

\begin{align}
 f(x)=q_o \rs^3 \left[\frac{x^{3-\delta}-1}{3-\delta}\right].
 \label{eq:massFlux}
\end{align}

@@

\begin{align}
\Phi&= -\frac{G \Menc}{r} - 4 \pi G \int_{r}^{\infty} \rhostar(r') r'
dr'.\nonumber\\
&\simeq -\frac{G \Menc}{r} -4 \pi G \int_{r}^{\rb} \rhostar(r') r' dr'
\label{eq:Phi}
\end{align}

Where in the scond line we have neglected the contribution of the
stars outside of the break radius, $\rb$, to the gravitational potential.

% Note our unconventional choice of gauge: the upper limit of the
% integral on the right hand side is $\rs$ whereas conventionally the
% upper limit is taken to be $\infty$. This means that our definition
% will not give $\Phi=0$ in the limit $r\rightarrow\infty$. However,
% our result for the enthalpy $\ke + \gammaf \frac{p}{\rho}$ will be
% gauge invariant.

Using equations~\eqref{eq:enConsInt},~\eqref{eq:massFlux},
and~\eqref{eq:Phi}, we may obtain an expression for the Bernoulli
parameter of the gas, $\ke+\gammaf \frac{p}{\rho} +\Phi$ of the gas inside
of the break radius $\rb$.

\begin{align}
  &\frac{v^2}{2}+\gammaf \frac{p}{\rho} +\Phi = \nonumber\\
  &-U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}

@@

\begin{multline}
  \frac{v^2}{2}+\gammaf \frac{p}{\rho}+\Phi
=\frac{G \Mbh}{\rs} 
\biggl[
  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2 -\delta} 
  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr].
\label{eq:enthAnal}
\end{multline}

@@

% For sufficiently large radii ($x$), the expression above always
% becomes negative, which means that a break in the stellar density
% profile is necessary in order to obtain an outflow.
 For a given $\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such
 that if $\zeta>\zeta_c$, an outflow will be possible from any
radius, since the Bernoulli parameter will be positive inside of the
break radius. On the other hand if $\zeta<\zeta_c$, then there is a
minimum value of $(\rs/\rsoi)_{\rm min}$. If we have had
$\rs/\rsoi<(\rs/\rsoi)_{\rm min}$, then the Bernoulli parameter would
become negative inside of $\rb$ and no outflow would be possible.

For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
($v_w\simeq\sigma_0$).  On the other hand for core galaxies
($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$, see the top
panel of Fig.~\ref{fig:zetaCrit}. For values of $\zeta<\zeta_c$, the
stagnation radius rapidly approaches the break radius as shown in the
bottom panel of Fig.~\ref{fig:zetaCrit}.
% We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
% for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
% less than this value the gas enthalpy would become negative inside of
% the break radius which is clearly unphysical.  This may be roughly
% approximated using (see Fig.~\ref{fig:rbRinf})

% \begin{align}
% &\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
% &\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
% \label{eq:rsRinfCrit}
% \end{align}

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} Mininmum value for ratio of the stagnation
  radius to the influence radius, $\rs/\rsoi$ for core galaxies
  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
  positive out to the break radius $\rb$. The solid lines correspond
  to the constraint computed numerically from
  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
  x-intercept of each curve corresponds to the critical $\zeta$,
  $\zeta_c$ above which an outflow is possible from any radius}
\end{figure}

### 2015-03-27 ms.tex
fixing a few typos
analytics...
more changes to the Bernoulli appendix.

Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
 \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[2
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
\label{eq:stag_analytic}
\end{align}

@@

... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1
  \times 10^{ -3 }}$ \\

@@

...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &
70 \\

@@

... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{
  -5 }$ & $ 7.2 \times 10^{ 3 }$ \\

@@

$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2
\times 10^{ -6 }$ & 99 & Conv\\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
    the ratio of the effective wind heating rate $v_{w}$ to the
    stellar velocity dispersion $\sigma$.  Green, orange, and blue
    symbols correspond to different values of $v_{w} =$ 300, 600, and
    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
    ($\Gamma = 0.1$). The black curves correspond to the analytic
    prediction from equation (\ref{eq:rs2main}), with solid and dashed
    curves calculated for parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
\end{figure}

@@

% Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.  Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.  What could cause this dependence?  Maybe Ia SNa...

% This is shown in the top panel Figure~\ref{fig:bh_xray}. The
% relationship from \citealt{Miller+15} and their detection
% upper limits are the black and blue solid lines
% respectively. The points correspond to the $\dot{M} c^2$ for our
% solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
% each galaxy.  We select $\vwO$=200 km/s, roughly the expected level of
% heating expected from main sequence the stellar winds and MSPs. If
% $L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
% bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
% 10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
% \citealt{Miller+15}.

% One possible solution that the wind mass loss rate $\eta$ increases
% with $\Mbh$, as would be expected if low mass SMBH preferentially
% hosted younger stellar populations.  Another possible explanation is
% that the effective heating rate of the CNM $v_{w}$ decreases
% with decreasing SMBH mass.  This could again be due to an older
% stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
% sources such as SN Ia and millisecond pulsars.
% {\bf AG given our new results on stellar wind heating as a function of
% Mbh. It seems like the first statement is indeed true but I suspect
% vwO actually increases for low Mbh and that this effect actually dominates.}
%, or it could be due to the fact that Ia occur too infrequently inside
%the stagnation radius for low mass black holes.
%AG-We now think that SNe Ia would become important only at the
%highest values of Mbh.
%AG-Note sure where the best place for this discussion would
%be--here or after presenting the comparisons with Miller et al.

%% AG:  Also want to include a plot of x-ray luminosity (less abstract than the accretion rate).

% \subsubsection{Comparison to measured temperature and density profiles}
% \citet{AllenDunn+:2006a} use {\it Chandra} X-ray observations to infer the radial temperature and density profiles in the nuclei of nine nearby X-ray luminous elliptical galaxies.  \citet{RussellMcNamara+:2013a} performed a similar analysis with a somewhat enlarged galaxy sample.  Interestingly, these works find a correlation between the accretion rate inferred assuming Bondi accretion and the AGN jet power, which is estimated by the PdV work required to inflate observed cavities in the X-ray emitting gas.  
% % At some point it would be useful to describe the differences between
% % these two sets of observations \citealt{RussellMcNamara+:2013a}
% % tries several different extrapolation schemes for the gas density,
% % and finds that that the uncertainty in extrapolating the density
% % profile is the dominant source of uncertainty in measuring the
% % accretion rate. Find total number which overlaps once the Russell
% % galaxies are included...

% Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.  We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.  The results of this exercise are presented in Fig.~\ref{fig:allen_compare}.

% Note that we have two free parameters ($\eta$ and $\vwO$) in our
% model, which implies that we can always match the observed temperature
% and densities at at least one point.  As a general rule, we find that
% a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
% with the observed temperatures.  We now highlight results for specific
% galaxies.
% % Thus, we choose $\vwO=500$ km/s.  We choose an
% % $\eta$ so that our solution would be consistent with the observed
% % density profiles. The comparison is shown in
% %% AG-The chosen properties, in particular eta may be summarized in a tabe.
% %% AG-Mention rising temperature profiles on large scales.

% \begin{itemize}
% % \item \emph{NGC4486} %eta=0.2
% %   On scales of $\sim1$ kpc the density profile in
% %   \citealt{AllenDunn+:2006a} is shallower than in our model. Our model
% %   has a break in the gas density at $\sim 300$ pc--near the location
% %   of the Nuker break radius for this galaxy at 560 pc. There is an
% %   observed break in the density, but on a scale of a few kpc.

% %   The temperature is assumed to be flat from the resolution limit
% %   inwards in \citealt{AllenDunn+:2006a}. However, in our models $T$
% %   increases monotonically towards the galactic center. This increase
% %   is due to the increased velocity dispersion (and thus increased
% %   heating) towards the galactic center.

% \item \emph{NGC5813} %eta=0.1 
%   The observed density profile (\citealt{RussellMcNamara+:2013a}) is
%   shallower than our calculated density profile, which has a sharp
%   break at $\sim$0.1 kpc, the location of the break radius in the
%   Nuker profile (this is the radius where the stellar light profile
%   transitions from a shallower inner power law slope to a steeper
%   outer power law slope).

%   For this galaxy we found that we could reproduce the observed
%   temperature on large scales with $\vwO=500$ km/s. The increased
%   velocity disperision towards the galactic center results in a sharp
%   increase in $T$ at small radii, which is not captured in the
%   observations due to resolution issues.
% \end{itemize}

% %It would be nice to have error bars for the observational points in this plot...
% \begin{figure*}
%   \includegraphics[width=\columnwidth]{NGC5813_T.eps}
%   \includegraphics[width=\columnwidth]{NGC5813_rho.eps}
%   \caption{\label{fig:allen_compare} Comparison of the radial profiles
%     (blue lines) of electron number density $n_e$ and temperature $T$
%     to the measured values (black square) in \citet{AllenDunn+:2006a}
%     and \citet{ RussellMcNamara+:2013a}. The dashed blue lines are
%     power law extrapolations of our profiles. Note that in going from
%     $\rho$ to $n_e$ we our adopted value for the molecular weight $\mu=1$.}
%   %% AG in the future we will have to be carfeful of the mean molecular weight.
% \end{figure*}

% \subsubsection{Comparison with observed X-ray Luminosity-Mass
%   Relation}
% %Note currently I reverse-engineer the stellar mass from the black
% %hole mass inferred from M-sigma; however, it would be better to use
% %the tabulated black hole mass from the Mbh-Mbulge relation.
% Fig.1 of \citealt{Miller+15} plots the observed
% relationship of unresolved x-ray luminosity versus galactic stellar
% mass for a sample of quiescent galaxies. We may construct a similar
% relationship with our own sample using the inferred accretion rates
% from our solutions.  To infer an x-ray luminosity for each solution,
% we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
% 10^{-7}$, which gives x-ray luminosities comparable to
% those in \citealt{Miller+15}. We also try an alternate
% prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
% take $L_x=2 \times 10^{-4} (\eddr) \Mdot c^2$.

% We must make choose a $\vwO$ for each galaxy.  We select $\vwO$=200
% km/s if $\rs<\rIa$ for this solution, $\vwO$=500 km/s if $\rs>\rIa$
% for this solution, or exclude it.  At low $\Mbh$ we have $\vwO$=200
% km/s and at high $\Mbh$ we have $\vwO$=500 km/s.  Note that much of
% our sample is excluded in this Fig., since for $\vwO$=200 km/s we
% would have $\rs>\rIa$ and four $\vwO$=500 km/s we would have
% $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$ would be
% inconsistent with the assumed level of heating).

% %AG-power law may be closer to 1.4 & 1.8 than to 1.5 & 2.
% Our results are plotted in Fig.~\ref{fig:bh_xray}. In our model
% there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
% \citealt{Miller+15}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{Miller+15} finds
% that $L_x \propto M_{\rm gal}^{0.7-0.8}$.

@@

% Apologies: 
% \begin{itemize}
% \item{we assume that average star formation histories correspond to those experienced in the nuclear region.  }

% \item{ Do nuclear star clusters in other galaxies look like scaled
%     up/down versions of the one in our own galaxy? If so this would
%     imply a radial gradient in the average of the stellar population
%     which would imply a heating which would be dependent on radius.  }

% \end{itemize}

% However, \citet{McCourt+12} argue that even if cooling is exactly
% balanced by heating everywhere, there is still a local thermal
% instability that operates to turn hot gas into cold clouds.  However,
% this local instability only causes a significant local drop-out of
% mass from the hot medium (to low-T clouds), if the cooling timescale,
% \begin{align}
% \frac{\tcool}{\tff} &\equiv \frac{3\rho k T/2 \mu \mp}{\dot{q}_{\rm cool}} \approx \frac{9}{5} \left. \frac{q \vw^2/2}{\dot{q}_{\rm cool}}\right|_{\rs}
% \end{align} 
% is locally shorter than the approximately 10 times the free-fall
% timescale $t_{\rm ff}$, where the last equality is evaluated at the
% stagnation radius and makes use of equations~(\ref{eq:Tanalytic}) and
% (\ref{eq:rhors2}).  We thus see that the condition $\tilde{v}_{w} \gtrsim v_{\rm
%   crit}$ is also the condition for local instability, although the
% prefactor may be slightly different.

% If cooling becomes important in the flow ($\tilde{v}_{w} < v_{\rm CI}$), it may lead to thermal instabilities.  There are two kinds of ``instabilities", global and local.  The global instability is simply that, if cooling becomes very rapid, the gas loses thermal pressure and starts to inflow faster, i.e. the entire CNM accretes.  In
% practice this should could manifest as a large increase in the stagnation radius, due an effective {\it decrease} in the effective heating rate.  This global ``instability" is not a true instability insofar as the gas does not necessarily clump locally into low-T clouds.

@@

  \section{Analytic expression for specific enthalpy of gas}
  {\bf AG: double check that what we are deriving here is actually
    specific enthalpy}
  \label{app:be}
  \input{be}

>>>>

Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
 \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[4
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
\label{eq:stag_analytic}
\end{align}

@@

... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1  \times 10^{ -3 }}$ \\

@@

...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ &70 \\

@@

... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\

@@

$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2\times 10^{ -6 }$ & 99 & Conv\\

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} Stagnation radius
    $r_{s}$ in units of the sphere of influence radius $r_{\rm soi}$
    (eq.~[\ref{eq:rsoi}]) for galaxies in our sample as a function of
    the ratio of the effective wind heating rate $v_{w}$ to the
    stellar velocity dispersion $\sigma$.  Green, orange, and blue
    symbols correspond to different values of $v_{w} =$ 300, 600, and
    1200 km s$^{-1}$, respectively.  Squares correspond to cusp
    galaxies ($\Gamma = 0.8$), while triangles correspond to cores
    ($\Gamma = 0.1$). The black curves correspond to the analytic
    prediction from equation (\ref{eq:rs2main}), with solid and dashed
    curves calculated for parameters $\{\Gamma=0.8, \densSlope\simeq1\}$ and
    $\{\Gamma=0.1,\densSlope\simeq0.6\}$, respectively. }
\end{figure}

@@

@@

@@

  \section{Analytic expression for Bernoulli parameter of gas}
  \label{app:be}
  \input{be}
